Joint Satellite Distributions in the Local Group

### 2017-09-26 paper/paper.tex
typos

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Satellites in the MW and M31]{Joint Satellite Distributions in the Milky Way and Andromeda}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{itemize}
\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two are considered as a pair. 
\item With $d_{AB}$ the distance between the two galaxies and
  $M_{\star,min}$ the lowest stellar mass in the two galaxies, we
  discard pairs that have any other galaxy $C$ with stellar mas
  $M_{\star}>M_{\star, min}$ closer than $3\times d_{AB}$ from any of
  the pair's members. 
\item The distance $d_{AB}$ greater than $700$ kpc.
\item The radial velocity between the two galaxies is $-120\ \kms <v_{AB,r}<0\ \kms$. 
\end{itemize}

We find $XX$ pairs with these conditions.

@@

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
of the satelites's geometric center $\bf{r}_{0}\equiv 1/N_s\sum_{k\in
  V} \bf{r}_i$, $\bf{1}$ is the unit matrix,  and  
${\bf r}^T$ is the transposed vector $\bf{r}$.

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$\hat{r}_{AB}$& & Unit vector along the direction connecting two
dominant galaxies\\
$N_s$ & & Number of satellites\\
$a > b> c$ & kpc & Inertia tensor eigenvalues. \\
$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
$\sigma_s$ & kpc & Ellipsoid width\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Satellites in the MW and M31]{Joint Satellite Distributions in
  the Local Group}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{itemize}
\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two are considered as a pair. 
\item With $d_{AB}$ the distance between the two galaxies and
  $M_{\star,min}$ the lowest stellar mass in the two galaxies, we
  discard pairs that have any other galaxy $C$ with stellar mas
  $M_{\star}>M_{\star, min}$ closer than $3\times d_{AB}$ from any of
  the pair's members. 
\item The distance $d_{AB}$ greater than $700$ kpc.
\item The relative radial velocity between the two galaxies, including
  the Hubble flow, is $-120\ \kms <v_{AB,r}<0\ \kms$. 
\end{itemize}

We find 32 pairs with these conditions. Figure shows the physical 
properties (stellar masses, maximum circular velocities, radial
velocities and separation) in those pairs.

@@

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
of the satelites's geometric center ${\bf r}_{0}\equiv \frac{1}{N_s}\sum_{k\in
  V} \bf{r}_i$, $\bf{1}$ is the unit matrix,  and  
${\bf r}^T$ is the transposed vector $\bf{r}$.

@@

\subsection{Satellites in the Local Group}

\subsection{Satellites in the Illustris Simulation}

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$\hat{r}_{AB}$& & Unit vector along the direction connecting two
dominant galaxies\\
$N_s$ & & Number of satellites\\
$a > b> c$ & kpc & Inertia tensor eigenvalues. \\
$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$ & & Inertia tensor eigenvectors. \\
$\sigma_s$ & kpc & Ellipsoid width\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}
